Looking for a Signal in the Noise: Revisiting Obesity and the Microbiome

### 2016-04-04 submission/Sze_Obesity_PeerJ_2016.Rmd

```{r Figure_2, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/"}
combinedData <- read.csv("results/tables/ROCcombinedData.csv", stringsAsFactors = FALSE)

@@

```{r Figure_3, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/"}

@@

```{r Figure_4, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/"}
# Section A
p1 <- ggplot(group.data.test, aes(obese, ZH))
p2 <- p1 + geom_boxplot(aes(fill = obese)) + scale_fill_brewer(palette="Set1")
p3 <- p2 + theme(axis.text=element_text(size=8), axis.title=element_text(size=10, face="bold"))
p4 <- p3 + xlab("") + ylab("Z-score Normalized H") + scale_x_discrete(breaks=c("No", "Yes"), labels=c("Non-Obese", "Obese"))
p5 <- p4 + guides(fill=FALSE)
p6 <- p5 + theme(axis.line=element_line(colour="black"),
                 panel.grid.major = element_blank(),
                 panel.grid.minor = element_blank(),
                 panel.border = element_blank(),
                 panel.background = element_blank())
p7 <- p6 + ggtitle('A') + theme(plot.title=element_text(hjust=0, face="bold", size=20))

@@

```{r Figure_5, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/"}

@@

```{r Figure_6, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/"}

>>>>

```{r Figure_2, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/", dev = c("pdf", "png")}
combinedData <- read.csv("results/tables/ROCcombinedData.csv", stringsAsFactors = FALSE)

@@

```{r Figure_3, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/", dev = c("pdf", "png")}

@@

```{r Figure_4, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/", dev = c("pdf", "png")}
# Section A
p1 <- ggplot(group.data.test, aes(obese, ZH))
p2 <- p1 + geom_boxplot(aes(fill = obese)) + scale_fill_brewer(palette="Set1")
p3 <- p2 + theme(axis.text=element_text(size=8), axis.title=element_text(size=10, face="bold"))
p4 <- p3 + xlab("") + ylab("Z-score Normalized H") + scale_x_discrete(breaks=c("No", "Yes"), labels=c("Non-Obese", "Obese"))
p5 <- p4 + guides(fill=FALSE)
p6 <- p5 + theme(axis.line=element_line(colour="black"),
                 panel.grid.major = element_blank(),
                 panel.grid.minor = element_blank(),
                 panel.border = element_blank(),
                 panel.background = element_blank())
p7 <- p6 + ggtitle('A') + theme(plot.title=element_text(hjust=0, face="bold", size=20))

@@

```{r Figure_5, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/", dev = c("pdf", "png")}

@@

```{r Figure_6, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/", dev = c("pdf", "png")}
